---
title: " "
---

# Data visualization examples

Please, see my data visualization portfolio below.

## 1. Ukraine crisis response (W3/W5)

```{r, echo = FALSE, warning = FALSE, message=FALSE}
options(knitr.duplicate.label = "allow")
#| echo : false
#| warning : false
library(openxlsx)
library(ggplot2)
library(dplyr)
library(plotly)
ds <- read.xlsx("https://docs.google.com/spreadsheets/d/e/2PACX-1vRCXWf-AF7nJPXmHUEstnkmEjDrkw-2bjdsjI4XQrHG28w2a5pm8Bk6aGPGz8VDOQwoBP7CaEagg0-R/pub?output=xlsx", sheet = 1)
```

One of the keys for providing consistent and timely support for affected populations, is the understanding of the presence and activities of humanitarian actors, working with affected populations.

```{r, echo = FALSE}
#| echo : false
ds_a <- ds %>% select(CCCM:WASH) %>% replace(is.na(.), 0) %>%  summarise_all(sum)
ds_a <- as.data.frame(t(ds_a))
#ds_a <- ds_a[, -1]
ds_a$cluster <- rownames(ds_a)
rownames(ds_a) <- NULL
ds_a <- ds_a |> filter(!(cluster %in% c("PROTECTION.TOTAL", "TOTAL"))) |> arrange(desc(V1))

p <- ggplot(ds_a, aes(x = cluster, y = V1))+
  geom_bar(stat = "identity")+
  coord_flip()+
  theme_minimal()+
  xlab(" ")+
  ylab("Total organizations in cluster")
ggplotly(p)
  
```

Please, do not hesitate to leave your comments in the section below:
